---
title: "Untitled"
author: "Hans Hinnershitz"
date: "8/15/2021"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Nine Functions
```{r}
library("readxl")
MIS510banks <- read_excel("MIS510banks.xlsx")
dim(MIS510banks)
head(MIS510banks)
View(MIS510banks)
mean(MIS510banks$Obs)
sd(MIS510banks$`Financial Condition`)
min(MIS510banks$`TotCap/Assets`)
max(MIS510banks$`TotExp/Assets`)
median(MIS510banks$`TotLns&Lses/Assets`)
length(MIS510banks$Obs)
```
## Linear Regression Model
```{r}
MIS510banks <- MIS510banks[, -c(1)]
MIS510banks$`Financial Condition` <- factor(MIS510banks$`Financial Condition`, levels = c(0,1), labels = c("Weak","Strong"))
logit.reg <- glm(`Financial Condition` ~ ., data = MIS510banks, family = "binomial")
options(scipen = 999)
summary(logit.reg)
```
### Estimated Logistic Equation

-686.10 - 13.71 TotCap/Assets + 3353.22 TotExp/Assets + 677.51 TotLns&Lses/Assets

Based off the estimated logistic equation, having a high TotCap/Assets ratio is negatively correlated with a bank that is defined as in a weak financial condition. In other words, the higher the TotCap/Assets ratio, the more likely the bank was in a strong financial position. The opposite was true of the other two variables, where TotExp/Assets and TotLns&Lses/Assets both were positively correlated with a weak financial condition.

#### Confusion Matrix

```{r}

logit.reg.pred <- predict(logit.reg,MIS510banks, type = "response")

data.frame(actual = MIS510banks$`Financial Condition`[1:5], predicted = logit.reg.pred[1:5])
```
##### Lift Chart
```{r}
library(gains)
MIS510banks <- read_excel("MIS510banks.xlsx")
MIS510banks <- MIS510banks[, -c(1)]
gain <- gains(MIS510banks$`Financial Condition`, logit.reg.pred, groups = length(logit.reg.pred))

plot(c(0,gain$cume.pct.of.total*sum(MIS510banks$`Financial Condition`)) ~ c(0,gain$cume.obs), xlab="# cases" , ylab = "Cumulative", main = "", type="l")
lines(c(0,sum(MIS510banks$`Financial Condition`))~ c(0,dim(MIS510banks)[2]), lty=2)

```

